Explorando la desigualdad politica: el rol de la comprension lectora

### 2020-05-28 docs/paper.Rmd
.

```{r}

@@

```{r}
regresion_miltinivel = if(is_html_output()) {
  regresion_html <-htmlreg(list(results_1,results_2,results_3, results_4, results_5 ))
} else if(is_latex_output()) {
  regresion_tex <-texreg(list(results_1,results_2,results_3, results_4, results_5 ))
}

>>>>

```{r include=FALSE}

@@

```{r include=FALSE}
regresion_miltinivel = if(is_html_output()) {
  regresion_html <-htmlreg(list(results_1,results_2,results_3, results_4, results_5 ))
} else if(is_latex_output()) {
  regresion_tex <-texreg(list(results_1,results_2,results_3, results_4, results_5 ))
}
